---
title: "Epistorm-mix"
author: "Chad Milando"
date: "2026-05-22"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Refs:

* https://github.com/epistorm/Epistorm-Mix/tree/main/matrices, 
* https://www.epistorm.org/data/epistorm-mix
* https://github.com/epistorm/Epistorm-Mix/tree/main/data/imputed_data


```{r}
xdir = "~/Documents/GitHub/Epistorm-Mix/tutorials/data-analysis/data/"
suppressMessages(library(tidyverse))
```

Lets do some random spot checks to see if this will work for our purposes

## Person 1

Lets look at the contact patterns for 1 person

```{r}
person_db <- read.csv(file.path(xdir, "imputed_resp.csv"))
subset(person_db, resp_id == 163925)
```

a 67 year old Female


Looking in the contact patterns db

```{r}
contact_db <- read.csv(file.path(xdir, "imputed_cont.csv"))
subset(contact_db, resp_id == 163925)
```

This persons *only* contact are:

* Household, 80yr Male
* Other, 25yr Female

Seems low?

## Person 2

Lets look at the contact patterns for 1 person

```{r}
subset(person_db, resp_id == 325231)
```

a 15 year old Male


Looking in the contact patterns db

```{r}
subset(contact_db, resp_id == 325231)
```

This persons *only* contact are:

* 3 household contacts
* and 6 school contacts
* and the teacher is 16

No contacts in "other" (the community setting)

and the school contacts seem low, both in other children and for teachers

## Population level 1-10

```{r}
pop_grp1 <- subset(person_db, resp_age %in% c(1:10))
all_contacts <- subset(contact_db, resp_id %in% c(pop_grp1$resp_id))
all_contacts %>%
  group_by(resp_id, cont_setting) %>%
  summarize(
    n = n()
  ) %>%
  ungroup() %>%
  group_by(cont_setting) %>%
  summarize(
    avg_n = mean(n)
  )

```

## Population level 60-65

```{r}
pop_grp1 <- subset(person_db, resp_age %in% c(60:65))
all_contacts <- subset(contact_db, resp_id %in% c(pop_grp1$resp_id))
all_contacts %>%
  group_by(resp_id, cont_setting) %>%
  summarize(
    n = n()
  ) %>%
  ungroup() %>%
  group_by(cont_setting) %>%
  summarize(
    avg_n = mean(n)
  )

```


## Population level 10-18

```{r}
pop_grp1 <- subset(person_db, resp_age %in% c(10:18))
all_contacts <- subset(contact_db, resp_id %in% c(pop_grp1$resp_id))
all_contacts %>%
  group_by(resp_id, cont_setting) %>%
  summarize(
    n = n()
  ) %>%
  ungroup() %>%
  group_by(cont_setting) %>%
  summarize(
    avg_n = mean(n)
  )

```
